Total Platform Cyber Protection

### 2016-08-21 paper.tex
think i fixed the biblio issue

Most research into hardware Trojans deal with using side-channel
analysis to identify the malicious Trojan behavior~\cite{lee2005,
agrawal2007, banga2008, banga2008a, jin2008, du2010, narasimhan2011,
narasimhan2012, cao2013, davoodi2013, dworak2013, forte2013,
liu2013, liu2014, bao2015}. This research uses power analysis, heat
analysis, or other side-effects to determine that the hardware is
executing abnormal logic. Unfortunately, this typically requires
building a model based on a ``golden'' or known-good hardware, which
is often not accessible. Furthermore, as chips become more complex,
the Trojan logic become an increasingly smaller portion of the chip,
which in turn reduces the side-channel behavior of the chip
significantly.

Other research has demonstrated the attacks that are possible by
actually implementing Trojan behavior~\cite{king2008, jin2010,
sturton2011, liu2013, jin2014, zhang2014}. This line of research
shows that Trojan logic is feasible for an attack.

@@

Another avenue of research is to change the design of the chip itself,
in order to improve the testability of the chip or to increase the
effectiveness of the side-channel analysis~\cite{chakraborty2008,
li2008, salmani2009, hicks2010, rosenfeld2011, waksman2011,
bhunia2013, davoodi2013, rajendran2013, rolt2014}. This line of
research attempts to rethink designing the hardware itself. However, a
major drawback is that this can increase the cost of the hardware and
it must be somehow mandated to be used in COTS components.

JTAG is a main avenue of reverse engineering hardware, so some work
has investigated the problem of securing JTAG access to
hardware~\cite{rosenfeld2010, ren2015}. The main idea is to allow only
authenticated users to have access to the JTAG functionality, however
this increases the cost and complexity of implemented JTAG.

@@

Finally, there are several surveys conducted on hardware security,
which provide a good overview of the field~\cite{wang2008,
tehranipoor2010, guin2014, guin2014a, guin2014b}.

@@

\subsection{Research}
%Faris: Some fixes below. 
Researchers have attempted to identify real-world attacks on firmware
code~\cite{tsow2006, cui2010, duflot2011, basnight2013, cui2013,
	zaddach2013, zaddach2013a, maskiewicz2014, stuttgen2015}. These
attacks are particularly effective, and researchers have shown that
these are able to persist through a reboot and cannot be detected by
the upper layers.

Other approaches are about how to prevent the tampering of
firmware~\cite{adelstein2002, zhou2007, zhou2009}. These protect from
the threat of tampering or altering the firmware, however it does not
address vulnerable firmware.

@@

Recent work has looked into the problem of updating the design of the
firmware so that it has security features, such as memory handling and
avoiding information leakage~\cite{koeberl2014, kauer2007}. However,
forcing firmware developers to use such features is an open issue.

@@

Recent work has looked into how to detect vulnerabilities in
firmware~\cite{davidson2013, costin2014, shoshitaishvili2015}. One of
these has an excellent website\footnote{\url{http://firmware.re}}
that contains the results of their reverse engineering and
vulnerability analysis~\cite{costin2014}.

>>>>

Most research into hardware Trojans deal with using side-channel
analysis to identify the malicious Trojan behavior~\cite{lee2005,
agrawal2007,banga2008,banga2008a,jin2008,du2010,narasimhan2011,
narasimhan2012,cao2013,davoodi2013,dworak2013,forte2013,
liu2013,liu2014,bao2015}. This research uses power analysis, heat
analysis, or other side-effects to determine that the hardware is
executing abnormal logic. Unfortunately, this typically requires
building a model based on a ``golden'' or known-good hardware, which
is often not accessible. Furthermore, as chips become more complex,
the Trojan logic become an increasingly smaller portion of the chip,
which in turn reduces the side-channel behavior of the chip
significantly.

Other research has demonstrated the attacks that are possible by
actually implementing Trojan behavior~\cite{king2008,jin2010,
sturton2011,liu2013,jin2014,zhang2014}. This line of research
shows that Trojan logic is feasible for an attack.

@@

Another avenue of research is to change the design of the chip itself,
in order to improve the testability of the chip or to increase the
effectiveness of the side-channel analysis~\cite{chakraborty2008,
li2008,salmani2009,hicks2010,rosenfeld2011,waksman2011,
bhunia2013,davoodi2013,rajendran2013,rolt2014}. This line of
research attempts to rethink designing the hardware itself. However, a
major drawback is that this can increase the cost of the hardware and
it must be somehow mandated to be used in COTS components.

JTAG is a main avenue of reverse engineering hardware, so some work
has investigated the problem of securing JTAG access to
hardware~\cite{rosenfeld2010,ren2015}. The main idea is to allow only
authenticated users to have access to the JTAG functionality, however
this increases the cost and complexity of implemented JTAG.

@@

Finally, there are several surveys conducted on hardware security,
which provide a good overview of the field~\cite{wang2008,
tehranipoor2010,guin2014,guin2014a,guin2014b}.

@@

\subsection{Research}
%Faris: Some fixes below. 
Researchers have attempted to identify real-world attacks on firmware
code~\cite{tsow2006,cui2010,duflot2011,basnight2013,cui2013,
zaddach2013,zaddach2013a,maskiewicz2014,stuttgen2015}. These
attacks are particularly effective, and researchers have shown that
these are able to persist through a reboot and cannot be detected by
the upper layers.

Other approaches are about how to prevent the tampering of
firmware~\cite{adelstein2002,zhou2007,zhou2009}. These protect from
the threat of tampering or altering the firmware, however it does not
address vulnerable firmware.

@@

Recent work has looked into the problem of updating the design of the
firmware so that it has security features, such as memory handling and
avoiding information leakage~\cite{koeberl2014,kauer2007}. However,
forcing firmware developers to use such features is an open issue.

@@

Recent work has looked into how to detect vulnerabilities in
firmware~\cite{davidson2013,costin2014,shoshitaishvili2015}. One of
these has an excellent website\footnote{\url{http://firmware.re}}
that contains the results of their reverse engineering and
vulnerability analysis~\cite{costin2014}.
